LAGOS lake depth

### 2020-02-26 figures/01_heatmap.Rmd
make a normalized heatmap

```{r 01_heatmap, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
library(corrr)
library(pheatmap)

@@

pretty_names <- gsub("mbgconhull_", "", names(dt_raw_ne))
pretty_names <- gsub("lake_", "", pretty_names)
pretty_names <- gsub("_nounits", "", pretty_names)
pretty_names <- gsub("focallake", "", pretty_names)

test <- dt_raw_ne %>%
  setNames(pretty_names) %>%
  dplyr::select_if(is.numeric) %>%
  dplyr::select(-lagoslakeid, -contains("decdeg"),
                -contains("nhd"),
                -contains("lagoslakeid"),
                -huc12) %>%
  correlate() %>%
  data.frame()
test_rowname    <- test$rowname
test            <- dplyr::select(test, -rowname)
row.names(test) <- test_rowname

pheatmap(t(test),
        color = colorRampPalette(
          RColorBrewer::brewer.pal(n = 7, name = "Reds"))(100))
```

>>>>

```{r 01_heatmap, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
library(corrr)
library(pheatmap)
library(recipes)

@@

dt_raw_ne_normal_rec <- recipe(. ~ ., data = dt_raw_ne) %>%
  step_normalize(all_numeric()) %>%
  prep()
dt_raw_ne_normal <- juice(dt_raw_ne_normal_rec)

create_heatmap <- function(x){
  print(range(x$lake_maxdepth_m))
  pretty_names <- gsub("mbgconhull_", "", names(x))
  pretty_names <- gsub("lake_", "", pretty_names)
  pretty_names <- gsub("_nounits", "", pretty_names)
  pretty_names <- gsub("focallake", "", pretty_names)

  test <- x %>%
    setNames(pretty_names) %>%
    dplyr::select_if(is.numeric) %>%
    dplyr::select(-lagoslakeid, -contains("decdeg"),
                  -contains("nhd"),
                  -contains("lagoslakeid"),
                  -huc12) %>%
    correlate() %>%
    data.frame()
  test_rowname    <- test$rowname
  test            <- dplyr::select(test, -rowname)
  row.names(test) <- test_rowname

  pheatmap(t(test),
          color = colorRampPalette(
            RColorBrewer::brewer.pal(n = 7, name = "Reds"))(100))
}

create_heatmap(dt_raw_ne)
create_heatmap(dt_raw_ne_normal)
```
